---
title: 'Homework #2'
author: "Aarushi Sahejpal, Jacika Patel, Rafael Saavedra"
date: "6/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(dplyr)
library(purrr)
library(magrittr)
library(base)
library(ggplot2)
```

```{r}
library(gapminder)
```


# 1) Instructions:   Follow the outline and the sequence of steps illustrated in the notes for creating a branch and pushing to Github.  After executing your steps in the  Bash terminal, produce images 1-5 and finally email your image 5 link  that gives evidence of a successful push and merge.  Also email a Word document that shows the steps and commands that you generated in the Bash terminal.

# Using the imbedded data table gapminder and appropriate dplyr functions, create an R file that contains code to create the following data table. Name this table gapminder1 and save it to your Bash Working Directory.


```{r}
gapminder1 <- gapminder %>%
mutate(logpop = log2(pop))

gapminder1
```

```{r}
gapminder1 <- filter(gapminder1, year == "1997" &
         continent == "Americas")
gapminder1
```

```{r}
gapminder1 <- gapminder1 %>%
arrange(desc(lifeExp))
gapminder1 
```

